PHQ-4-R: Adaptation of the 4-item screening for Anxiety and Depression for a subclinical sensitivity

### 2023-03-14 analysis.Rmd
add primals

```{r, message=FALSE, warning=FALSE}
pi <- make_correlation(df[vars], select(df, starts_with("PI_")))
export_table(pi$print)
gcbs <- make_correlation(df[vars], select(df, starts_with("GCBS_"))) 
export_table(gcbs$print)
age <- make_correlation(df[vars], data.frame(Age = df$Age)) 
export_table(age$print)
sex <- make_correlation(df[vars], data.frame(Sex = ifelse(df$Sex == "Male", 0, 1)) )
export_table(sex$print)
```

@@

  mutate(gcbs$data, Domain = "Conspiracy Beliefs")

@@

         Domain = fct_relevel(Domain, "MAIA", "Normal Personality", "Maladaptive Personality", "Autistic Traits", "Schizotypic Traits"),
         Parameter2 = str_remove_all(Parameter2, "MAIA_|IPIP6_|PID5_|ASQ_|SPQ_|GCBS_|PHQ4_"),

@@

  scale_alpha_manual(values = c(0.2, 1)) +

@@

fig <- ((wrap_elements(p_dens) + wrap_elements(p_efa)) / p_graph)
ggsave("figures/Figure1.png", fig, width=fig.width, height=fig.width*1.3, dpi=150)
ggsave("figures/Figure2.png", p_cor, width=21*0.35, height=29.7*0.35, dpi=150, bg="white")
```

>>>>

```{r, message=FALSE, warning=FALSE}
pi <- make_correlation(df[vars], select(df, starts_with("PI_")))
export_table(pi$print)
lie <- make_correlation(df[vars], select(df, starts_with("LIE_")))
export_table(lie$print)
gcbs <- make_correlation(df[vars], select(df, starts_with("GCBS_"))) 
export_table(gcbs$print)
age <- make_correlation(df[vars], data.frame(Age = df$Age)) 
export_table(age$print)
sex <- make_correlation(df[vars], data.frame(Sex = ifelse(df$Sex == "Male", 0, 1)) )
export_table(sex$print)
```

@@

  mutate(bpd$data, Domain = "Mood"),
  mutate(gcbs$data, Domain = "Conspiracy Beliefs"),
  mutate(pi$data, Domain = "World Beliefs"),
  mutate(lie$data, Domain = "Lying Profile")

@@

         Domain = fct_relevel(Domain, "MAIA", "Normal Personality", "Maladaptive Personality", "Autistic Traits", "Schizotypic Traits", "Mood", "Lying Profile", "Conspiracy Beliefs", "World Beliefs"),
         Parameter2 = str_remove_all(Parameter2, "MAIA_|IPIP6_|PID5_|ASQ_|SPQ_|GCBS_|PHQ4_|LIE_|PI_"),

@@

  scale_alpha_manual(values = c(0.3, 1)) +

@@

fig <- ((wrap_elements(p_dens) + wrap_elements(p_efa)) / p_graph)
ggsave("figures/Figure1.png", fig, width=fig.width, height=fig.width*1.3, dpi=200)
ggsave("figures/Figure2.png", p_cor, width=21*0.35, height=29.7*0.44, dpi=200, bg="white")
```
